% !Mode:: "TeX:UTF-8"

%%%---- 郑重声明 (无需改动)------------------------------------%

\thispagestyle{empty}
\vspace*{20pt}
\begin{center}
	{\ziju{0.8}\pmb{\songti\zihao{2} 郑重声明}}
\end{center}
\par\vspace*{30pt}
\renewcommand{\baselinestretch}{2}
{\zihao{4}%
	
本人呈交的设计报告，是在指导老师的指导下，独立进行实验工作所取得的成果，
所有数据、图片资料真实可靠。 尽我所知，除文中已经注明引用的内容外，
本设计报告不包含他人享有著作权的内容。
对本设计报告做出贡献的其他个人和集体，
均已在文中以明确的方式标明。本设计报告的知识产权归属于培养单位。\\[2cm]
	
	\hspace*{1cm}本人签名: $\underline{\hspace{3.5cm}}$
	\hspace{2cm}日期: $\underline{\hspace{3.5cm}}$\hfill\par}
%------------------------------------------------------------------------------

\renewcommand{\baselinestretch}{1.5}  %下文的行距

\begin{cnabstract}
网络技术随着硬件的发展逐步提高，用户对高质量网络办公需求的情感越来越强，用户可以从中获取海量有用的信息，减少时间和资源的浪费。互联网在我国的政治、经济、生活上产生了非常大的影响，开发一款在线文本共享编辑系统可以有效地降低人们对办公位置的需求和限制，以此来实现居家办公的愿景。结合元宇宙、共享场景等概念，在线文本共享编辑成为了办公、学习、工作、国际交流的主流方式之一。本系统以python作为开发环境，pycharm为编译软件，结合MinIO和mysql分别作为文件管理系统和数据库管理系统，设计开发一款在线文档共享编辑系统。前端部分使用tkinter模块生成，后端模块通过flask框架接口生成。


\end{cnabstract}
\par
\vspace*{2em}

\cnkeywords{在线文档; 数据库; 服务器; flask }

\begin{enabstract}
With the gradual improvement of network technology with the development of hardware, users are more and more emotional about the demand for high-quality network office, and users can obtain a large amount of useful information from it, reducing the waste of time and resources. The Internet has had a great impact on our country's politics, economy and life. The development of an online text sharing editing system can effectively reduce people's needs and restrictions on office locations, so as to realize the vision of working from home. Combined with concepts such as metaverse and shared scenes, online text sharing and editing has become one of the mainstream ways of office, study, work, and international communication. This system uses python as the development environment, combined with MinIO and mysql as the file management system and database management system respectively, to design and develop an online document sharing and editing system. The front-end part is generated using the tkinter module, and the back-end module is generated through the flask framework interface.
	
	
\end{enabstract}
\par
\vspace*{2em}
\enkeywords{Online documents; database; server; flask}\\

\newpage
\cleardoublepage

\renewcommand{\baselinestretch}{1.5}
